Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-26 ms.tex
fixed 2.1

We fix $\beta = 2$ but have our results are not overly sensitive to
the properties of the gas flow on radial scales $\gtrsim r_b$ for
$\beta\gsim 1.5$ (this is near the peak of the distribution of $\beta$
in \citet{LauerFaber+:2007a}) {\bf AG: a little more detail}. The
presence of the break radius $r_{b}$ is, however, necessary to obtain
a converged steady state for some regions of our parameter space.  We
consider solutions calculated for up to four values of $\rb$: 50 pc,
100 pc, 200 pc, and 400 pc, motivated by the range of break radii from
the \citet{LauerFaber+:2007a} sample.\footnote{For the core galaxies
  the break radius follows the scaling relationship $\rb\sim 106 \,
  (\Mbheight)^{0.39}$ pc, with scatter of approximately one dex.  Most
  the cusp galaxies have $\rb$ between 100 and 1000 pc, and lack a
  clear trend with $\Mbh$.}  In practice we calculate solutions for a
range of $\rb$ only in cases when its precise value is expected to
have a significant affect on the solution, in particular for high SMBH
masses and low heating rates, for which the stagnation radius
approaches large radii. We also neglect values of $r_b$ which would
give unphysically large bulges for a given $\Mbh$.

For low mass galaxies, nuclear star clusters $\Mbh\lsim 2\times 10^8
\Msun$ may be present \citep{GrahamSpitler:2009a}.  Mass injection to
the nucleus could (for $\Mbh\lsim 2 \times 10^{8} \Msun$) therefore be
dominated by a nuclear star cluster with its own break radius on
parsec scales, i.e. much smaller than our fiducial value of $r_b \sim
100$ pc. However, for high heating rates the stagnation radius is not
sensitive to the location of the break radius, and out models could
also describe the accretion rate in the case of a nuclear star cluster.

>>>>

We fix $\beta = 2$ but find that our results are not overly sensitive to
the properties of the gas flow on radial scales $\gtrsim r_b$ for values of
$\beta\gsim 1.5$, which characterize most of the \citet{LauerFaber+:2007a} sample.  The
presence of the break radius $r_{b}$ is, however, necessary to obtain
a converged steady state for some regions of our parameter space.  We
consider solutions calculated for up to four values of $\rb$: 50 pc,
100 pc, 200 pc, and 400 pc, motivated by the range of break radii from
the \citet{LauerFaber+:2007a} sample.\footnote{For the core galaxies
  the break radius follows the scaling relationship $\rb\sim 106 \,
  (\Mbheight)^{0.39}$ pc, with scatter of approximately one dex.  Most
  the cusp galaxies have $\rb$ between 100 and 1000 pc, and lack a
  clear trend with $\Mbh$.}  In practice we calculate solutions for a
range of $\rb$ only in cases when its precise value is expected to
have a significant affect on the solution, in particular for high SMBH
masses and low heating rates, for which the stagnation radius
approaches large radii. We also neglect values of $r_b$ which would
give unphysically large bulges for a given $\Mbh$.

Finally, we note that some low mass galaxies with $\Mbh\lsim 2 \times 10^{8} \Msun$ possess nuclear star clusters (\citealt{GrahamSpitler:2009a}), which are not accounted for by our simple parametrization of the stellar density.  In such cases gas and energy injection could be dominated by the cluster itself, i.e. concentrated within its own pc-scale ``break radius" which is much smaller than the outer break in the older stellar population on much larger scales.  If the extent of the cluster is known, however, our model can be fully generalized to this case.  Furthermore, for high heating rates the stagnation radius and concomitant accretion rate are not sensitive to the location of the break radius.
